---
title: "gapminder"
author: "Wilson Leung"
date: "23/03/2021"
output: pdf_document
---

```{r setup, include=FALSE}
# tinytex::install_tinytex()
# install.packages("tidyverse")
# install.packages("gapminder")
library(gapminder)
library(tidyverse)

library(dplyr)


knitr::opts_chunk$set(echo = TRUE)
```

---

## Introduction 

In this document we will be exploring the Gapminder dataset 


## Observations of gapminder


### Countries with life expectancy less than 30 
```{r Step 12}
gapminder %>% filter(lifeExp<30)


```

### Key observations

* The observation is from 1952 and 1992 for Afghanistan and Rwanda respectively
* There is only 2 observations


### Countries with life expectancy greater than 81

```{r Step 13}

gapminder %>% filter(lifeExp>81)


```



### Life expectancy by continent in 2007


```{r Boxplot}

gapminder_2007<-gapminder%>%  filter(year==2007)

boxplot(gapminder_2007$lifeExp ~gapminder_2007$continent)

```


#### Key Observations

* African life expectancies are quite varied but the median is the lowest across all continents
* Oceania has the least varied life expectancy



---


